Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-11-05 Manuscript/manuscriptPGPEsuppl.tex

\section{Comparison of headgroup order parameters from different force fields to experiments}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPE.pdf}
  \caption{\label{HGorderParametersPE}
    The headgroup and glycerol backbone order parameters of PE lipids
    from experiments (POPE and signs this work, DPPE from Ref.~\citenum{seelig76}
    and E.coliPE from Ref.~\citenum{gally81}) and simulations with different force fields.
  }
  \todo{This should be clarified as in NMRlipidsI and error bars should be added.
    Probably larger error bars for united atom models based on the report by Fuchs et al.
  } \\
\end{figure}

>>>>

\section{Comparison of headgroup order parameters from different force fields to experiments}
The poor performance of headgroup order parameters in Berger model can be probably explained by
ring like structures seen in Fig. 6 in Ref. \citenum{mukhopadhyay04}, which is a typical feature
for Berger based lipid force fields containing explicit hydrogen atoms in the head group \cite{zhao08,henin09,dahlberg10}.
The poor performance of glycerol backbone of Slipids simulations is systemically observed also
for other lipids in previous studies \cite{botan15,antila19}.
\todo{Should we comment more the relative quality of different force fields and/or make the subjective force field ranking figures?
https://github.com/NMRLipids/NMRlipidsIVPEandPG/issues/8}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPE.pdf}
  \caption{\label{HGorderParametersPE}
    The headgroup and glycerol backbone order parameters of PE lipids
    from experiments (POPE and signs this work, DPPE from Ref.~\citenum{seelig76}
    and E.coliPE from Ref.~\citenum{gally81}) and simulations with different force fields.
  }
  \todo{This should be clarified as in NMRlipidsI and error bars should be added.
    Probably larger error bars for united atom models based on the report by Fuchs et al.
  } \\
\end{figure}
